% Separate title page for a double-anonymous submission.
% This file is NOT \input into main.tex; compile it on its own and upload it
% as the non-anonymous title page. Fill the bracketed fields before submitting.
\documentclass[12pt]{article}
\input{preamble}

\title{\bfseries Democracy and Nationalism, Reconsidered}
\author{Steven Denney\\[2pt]
\normalsize [Affiliation, City, Country]\\
\normalsize ORCID: [0000-0000-0000-0000]}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}
\singlespacing

\noindent\textbf{Corresponding author.} Steven Denney, [email], [postal address].

\bigskip
\noindent\textbf{Acknowledgments.} [Seminar audiences, colleagues, and data providers to thank.]

\bigskip
\noindent\textbf{Funding.} [Name the funding source and grant number, or: This research received no specific grant from any funding agency in the public, commercial, or not-for-profit sectors.]

\bigskip
\noindent\textbf{Conflicts of interest.} The author declares none.

\bigskip
\noindent\textbf{Use of AI.} [Disclose any generative-AI tools used in the research or writing, and how, per the journal's policy at submission.]

\bigskip
\noindent\textbf{Ethics.} This study analyzes secondary, publicly archived, and de-identified survey data, and did not require human-subjects review.

\bigskip
\noindent\textbf{Data availability.} ISSP 2023 (ZA10010) and the earlier ISSP National Identity rounds are publicly available from the GESIS Data Archive; V-Dem v15 is accessed through the \texttt{vdemdata} R package. Replication code accompanies the submission and will be deposited in the JOP Dataverse on acceptance.

\bigskip
\noindent\textbf{Word count.} [Insert final count: main text excluding abstract, notes, and references.]

\end{document}
